### 2023-01-03 output/summary_statistics/tables/summary_statistics.tex
Added median to summary statistics
Created treatment timing table

\begin{tabular}{llccc}
\toprule
 &  & Median & Mean & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.00 & 0.12 & 0.32 & 40,727 \\
 & For cause (transfer) & 0.00 & 0.01 & 0.08 & 40,727 \\
 & Foreclosure & 0.00 & 0.02 & 0.14 & 40,727 \\
 & Foreclosure (transfer) & 0.00 & 0.00 & 0.03 & 40,727 \\
 & No cause & 0.00 & 0.10 & 0.30 & 40,727 \\
 & No cause (transfer) & 0.00 & 0.01 & 0.08 & 40,727 \\
 & Non-payment of rent & 1.00 & 0.73 & 0.44 & 40,727 \\
 & Non-payment of rent (transfer) & 0.00 & 0.02 & 0.13 & 40,727 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 21.00 & 57.81 & 78.29 & 39,087 \\
 & Case defaulted & 0.00 & 0.20 & 0.40 & 40,727 \\
 & Case involuntarily dismissed & 0.00 & 0.29 & 0.45 & 40,727 \\
 & Case heard & 0.00 & 0.06 & 0.23 & 40,727 \\
 & Case mediated & 0.00 & 0.41 & 0.49 & 40,727 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.00 & 0.09 & 0.28 & 40,727 \\
 & Plaintiff has an attorney & 1.00 & 0.84 & 0.37 & 40,727 \\
 & Defendant is an entity & 0.00 & 0.01 & 0.08 & 40,727 \\
 & Plaintiff is an entity & 1.00 & 0.70 & 0.46 & 40,727 \\
 & Money judgment & 0.00 & 1890.34 & 5279.49 & 40,727 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 775200.00 & 9435708.78 & 20612629.31 & 14,491 \\
 & Building value & 190000.00 & 2482603.38 & 6470958.91 & 14,491 \\
 & Land value & 2600.00 & 113817.19 & 536568.37 & 14,491 \\
 & Other value & 1067000.00 & 12020146.88 & 26285935.89 & 14,491 \\
 & Units & 1.00 & 42.25 & 112.87 & 14,491 \\
\cline{1-6}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 213270.60 & 261462.86 & 238040.64 & 9,842 \\
 & Four years before latest docket date & 225065.75 & 280243.32 & 276051.45 & 9,968 \\
 & Three years before latest docket date & 240097.38 & 307137.16 & 369763.53 & 10,172 \\
 & Two years before latest docket date & 259176.00 & 341084.08 & 987145.51 & 10,182 \\
 & One year before latest docket date & 278722.25 & 351172.05 & 311982.74 & 10,190 \\
 & Latest docket date & 305144.00 & 377384.02 & 316645.29 & 10,096 \\
 & One year after latest docket date & 347550.00 & 421601.75 & 344328.86 & 10,443 \\
 & Two years after latest docket date & 393900.00 & 477948.08 & 457694.83 & 9,175 \\
 & Three years after latest docket date & 414600.00 & 501611.80 & 780467.01 & 5,894 \\
\cline{1-6}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccc}
\toprule
 &  & Median & Mean & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.00 & 0.12 & 0.32 & 40,727 \\
 & For cause (transfer) & 0.00 & 0.01 & 0.08 & 40,727 \\
 & Foreclosure & 0.00 & 0.02 & 0.14 & 40,727 \\
 & Foreclosure (transfer) & 0.00 & 0.00 & 0.03 & 40,727 \\
 & No cause & 0.00 & 0.10 & 0.30 & 40,727 \\
 & No cause (transfer) & 0.00 & 0.01 & 0.08 & 40,727 \\
 & Non-payment of rent & 1.00 & 0.73 & 0.44 & 40,727 \\
 & Non-payment of rent (transfer) & 0.00 & 0.02 & 0.13 & 40,727 \\
\cline{1-6}
\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 0.20 & 0.40 & 40,727 \\
 & Case duration & 21.00 & 57.81 & 78.29 & 39,087 \\
 & Case heard & 0.00 & 0.06 & 0.23 & 40,727 \\
 & Case involuntarily dismissed & 0.00 & 0.29 & 0.45 & 40,727 \\
 & Case mediated & 0.00 & 0.41 & 0.49 & 40,727 \\
 & Money judgment & 0.00 & 1890.34 & 5279.49 & 40,727 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.00 & 0.09 & 0.28 & 40,727 \\
 & Defendant is an entity & 0.00 & 0.01 & 0.08 & 40,727 \\
 & Plaintiff has an attorney & 1.00 & 0.84 & 0.37 & 40,727 \\
 & Plaintiff is an entity & 1.00 & 0.70 & 0.46 & 40,727 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 192400.00 & 2471065.61 & 6218383.08 & 36,587 \\
 & Land value & 1000.00 & 112575.80 & 659661.29 & 36,587 \\
 & Other value & 954900.00 & 10900678.30 & 26482630.60 & 36,587 \\
 & Total property value & 636500.00 & 8350204.19 & 22073916.94 & 36,587 \\
 & Units & 0.00 & 40.76 & 157.57 & 36,587 \\
\cline{1-6}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 213270.60 & 261462.86 & 238040.64 & 9,842 \\
 & Four years before latest docket date & 225065.75 & 280243.32 & 276051.45 & 9,968 \\
 & Latest docket date & 305144.00 & 377384.02 & 316645.29 & 10,096 \\
 & One year after latest docket date & 347550.00 & 421601.75 & 344328.86 & 10,443 \\
 & One year before latest docket date & 278722.25 & 351172.05 & 311982.74 & 10,190 \\
 & Three years after latest docket date & 414600.00 & 501611.80 & 780467.01 & 5,894 \\
 & Three years before latest docket date & 240097.38 & 307137.16 & 369763.53 & 10,172 \\
 & Two years after latest docket date & 393900.00 & 477948.08 & 457694.83 & 9,175 \\
 & Two years before latest docket date & 259176.00 & 341084.08 & 987145.51 & 10,182 \\
\cline{1-6}
\bottomrule
\end{tabular}
